---
title: "Pollution Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pollution Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## **1 Introduction:**
<p class="justify">Pollution monitoring is a critical practice that provides real-time insights into the dynamic and often invisible threats posed by pollutants. Regular monitoring helps us comprehend the magnitude and spatial distribution of pollutants, enabling timely responses to mitigate risks. By understanding pollution trends, we can assess the effectiveness of pollution control measures, adapt policies, and raise awareness among communities.</p>
<p class="justify">The "SAWpollut" R package serves as an invaluable asset in this endeavor. Its diverse functions offer a comprehensive toolkit for analyzing, visualizing, and understanding pollution data across different contexts. From identifying pollution hotspots to uncovering seasonal variations and exploring relationships between pollutants, the package equips users with tools to extract meaningful insights. The package streamlines the exploration of complex pollution data, fostering informed decision-making for researchers, policymakers, and environmental professionals. As pollution increasingly threatens our health and ecosystems, the "SAWpollut" package plays a pivotal role in providing actionable information to address these challenges effectively and promote a healthier, more sustainable future.</p>
  
## **2 Data Description**
  <p class="justify">This dataset encompasses comprehensive air pollution measurement data within Seoul, South Korea. By meticulously compiling and refining diverse air pollution-related datasets furnished by the Seoul Metropolitan Government, a structured and coherent dataset has been curated. The dataset furnishes averaged records for six distinct pollutants, namely SO2, NO2, CO, O3, PM10, and PM2.5. Additionally, the versatility of this dataset extends beyond air pollution, encompassing the potential for integrating soil pollution and water pollution data using the same comprehensive package.</p>
  <p class="justify">The measurements were conducted on an hourly basis throughout the entirety of 2019, providing a granular understanding of pollution levels. This extensive dataset covers air quality observations across 25 distinct districts within the city of Seoul. Researchers and analysts can harness this data to unravel intricate trends, identify pollution sources, and derive valuable insights into the environmental landscape of Seoul. The inclusion of soil and water pollution data further enriches the dataset's potential, enabling a holistic examination of various pollution vectors and their interconnections.</p>
### 2.1 Installation
Install the package, then load the data and function-containing library.
```{r setup}
library(SAWpollut)
```

### 2.2 Setting up the environment
The "load_data" function, included in the package, serves the purpose of loading pollution data stored within the package's data directory. By calling this function, users can access a data frame containing pollution-related information. The function employs the system.file command to locate the pertinent CSV file within the package. Once located, the data is read using read.csv, and the resulting data frame is returned for analysis. This function streamlines the process of accessing and integrating pollution data into analytical workflows, allowing users to quickly delve into pollution-related investigations without the hassle of manually sourcing and reading external files.

```{r}
pollution_data <- load_data()
data <- load_data()
print(head(pollution_data))
```

## **3 Results and discussion**

In this part, I've shown how to use every function I've developed to evaluate pollution data and provide plots and data frames as output.

### 3.1 Location with Highest Pollutant Concentrations
The `highpol` function, intended for export, aims to identify the highest pollutant concentration data points within a CSV file. Upon reading the file, the function processes the provided list of pollutants. For each pollutant, it locates the row with the maximum concentration value, extracts the corresponding address, and structures the result as a list. The overall outcome is a list containing pollutant-specific sublists, each holding the address associated with the highest concentration occurrence for that pollutant. This function aids users in quickly pinpointing addresses where pollutants have reached their peak levels, facilitating targeted investigation and response efforts in areas of concern.

```{r}
file <- load_data
pollutants= c("CO", "SO2", "NO2", "O3")
pollu_locs <- highpol(file, pollutants)
for (pollutant in pollutants) {
  cat("Pollutant:", pollutant, "\n")
  cat("Address:", pollu_locs[[pollutant]]$address, "\n\n")}
```

### 3.2 Interpolation
The `intpol` function is designed to perform spatial interpolation and visualization of pollutant concentrations based on data from a CSV file. After reading the file, the function generates longitude and latitude grids spanning the range of the data. It then uses the Akima package to interpolate pollutant concentration values across the defined grid. The interpolated values are plotted using the `image` function, creating a color-coded representation of pollutant concentrations on a spatial grid. Contour lines are added to provide additional visual cues. Existing measuring station locations are marked in red using circle markers, allowing users to compare measured values with the interpolated ones. Overall, the function facilitates understanding and visual exploration of pollutant concentration patterns across a geographic area, enhancing insights into spatial trends and potential pollution hotspots.
```{r,fig.height=6,fig.width=6}
data <- load_data()
intpol(data, "PM10")
```

### 3.3 Daily to Annual Pollution Conversion
The `d2a_conv` function is designed to transform a CSV dataset containing timestamped pollutant measurements into an annual aggregated format. After reading the file, the function converts the specified date column into a Date object and extracts the year information. It then calculates the mean pollutant levels for each year and creates a new aggregated dataset. The returned dataset presents annual averages for the selected pollutants, allowing users to gain insights into long-term trends and changes in pollution levels over time.
```{r}
data <- load_data()
pollutants <- c("SO2", "NO2", "O3", "CO", "PM10", "PM2.5")
d2a_conv(data = data, date = "Date", pollutants = pollutants)
```

### 3.4 Cluster Analysis of Pollutant Profiles
The `clust` function facilitates clustering analysis on a given CSV dataset containing pollutant measurements. Users can choose between the "kmeans" clustering method or receive an error message for unsupported methods. The function reads the file, extracts the specified pollutants' data, and applies k-means clustering if selected. It displays the clustering results and, if there are multiple clusters, generates a cluster plot with distinctive colors for each cluster. Users can customize the number of clusters using the 'k' parameter. The function aids in understanding pollutant profiles' similarity patterns, allowing for informed decision-making based on cluster memberships.
```{r, fig.height=6,fig.width=6}
data <- load_data()
pollutants <- c("PM10", "PM2.5")
clust(data, pollutants, method = "kmeans", k = 4)
```

### 3.5 Daily, Monthly Time Series Plot
The `dm_plots` function is designed to visualize time series data from a CSV file, particularly focused on pollutant measurements. After reading the file, the function converts the specified date column into a Date object. It then aggregates the data into daily, monthly, and annual time series formats. For each of the specified pollutants, the function generates plots: first, it displays the daily time series with a line plot, and then it creates a monthly time series plot using a combination of lines and points for better visibility. These plots help users observe trends and variations in pollutant concentrations on both a daily and monthly basis, facilitating the analysis of temporal patterns and potential seasonality in the data.
```{r}
data <- load_data()
dm_plots(data, "Date", pollutants = c("SO2", "NO2", "O3", "CO", "PM10", "PM2.5"))
```

### 3.6 Anomaly Detection
The `anomaldet` function is designed for detecting and visualizing anomalies in time series data related to pollutants. It takes a CSV file with timestamped measurements, identifies anomalies by applying ARIMA modeling and comparing residuals to a threshold, and then generates a plot that showcases the original time series, forecasted values, and detected anomalies. The function's parameters allow customization of forecasting horizon, ARIMA order, and anomaly threshold. By offering a comprehensive view of anomalies in the context of the time series, the function aids in understanding and addressing irregularities in pollutant data patterns. 
```{r,fig.height=6,fig.width=6}
data <- load_data()
anomaldet(data, date_col = "Date", pollutant = "PM10",forecast_horizon = 24, 
                             arima_order = c(1, 1, 1), threshold = 2.5)
```

### 3.7 Matrix Plot
The "matplot" function, part of the package, offers a dynamic way to visualize relationships between pollutants through a matrix plot. By utilizing this function, users can swiftly create a comprehensive matrix plot that visually portrays the correlations between selected pollutants. The function takes input in the form of a data frame containing pollutant data and a vector of pollutant names to be included in the matrix plot. After selecting the relevant pollutant columns, the function calculates the correlation matrix among these pollutants using complete observations. The matrix plot facilitates the identification of patterns and interactions among pollutants, aiding users in gaining a clearer understanding of how different pollutants relate to one another.
```{r}
data <- load_data()
pollutants <- c("SO2", "NO2", "O3", "CO", "PM10", "PM2.5")
matriplot(data, pollutants)
```

### 3.8 Seasonal Analysis
The `seaso` is designed to analyze and visualize the seasonal variations of pollutant levels within a CSV dataset. It performs Longitudinal analysis. After reading the file, it converts the "Date" column into a Date object and extracts year and month information. The function then defines seasons based on the months, categorizing them into Spring, Summer, Fall, and Winter. It initializes an empty data frame to store results and processes each specified pollutant. For each pollutant, the function calculates the average levels for each year and season and stores them in a separate data frame. It merges these results with the main data frame and subsequently generates bar plots for each pollutant, illustrating the average levels over the years and seasons. This allows users to gain insights into the seasonal patterns of pollutant concentrations, aiding in understanding the temporal trends and variations in air quality. The function returns a data frame containing the calculated average levels for further analysis.
```{r}
data <- load_data()
pollutants <- c("SO2", "NO2", "O3", "CO", "PM10", "PM2.5")
seaso(data, pollutants)
```

### 3.9 Correlation and Regression Analysis
The `correg` function computes the correlation and regression analysis between pairs of specified pollutants in a given CSV dataset. It reads the file, iterates through the provided pollutants, and for each pair, calculates the Pearson correlation coefficient to assess their linear relationship. It further computes the slope and intercept of the regression line to model one pollutant's potential prediction based on the other. The function then prints the correlation, regression equation, and displays scatter plots with regression lines for each pair of pollutants. This functionality helps users comprehend the statistical association and predictive relationship between chosen pollutants, fostering insights into potential dependencies within environmental or experimental data.
```{r}
data <- load_data()
pollutants <- c("SO2", "NO2", "O3", "CO", "PM10", "PM2.5")
correg(data, pollutants)
```

## **4 Conclusion**
The "SAWpollut" R package is a versatile tool for analyzing pollution data across soil, air, and water domains. It offers features like anomaly detection, clustering, correlation analysis, temporal aggregation, and seasonal variation assessment. This package aids researchers, analysts, and policymakers in deriving insights from pollution datasets and making informed decisions. Its user-friendly functions facilitate data integration and exploration, making it a valuable resource for uncovering patterns and trends in pollution measurements. Overall, "SAWpollut" empowers users to contribute to environmental understanding and promote sustainable solutions.
